%Write introduction \cite{8625938}.

Formal verification of cyber-physical systems can be a daunting task due to the \emph{state
explosion problem} \cite{Clarke2012}. We tackle this challenge from two angles. First, we use a
compositional verification technique \cite{pnueli} \cite{cmc} to decompose the reasoning on the global state space into a
number of localized problems for each component separately. The system proof is constructed
from the individual component proofs. Second, we assume the components execute in a static 
sequential order. We do not consider all possible execution orders; in other words, non-determinism
due to scheduling decisions is excluded. In fact, in many safety-critical applications the actual
implementation executes according to a pre-defined schedule \cite{executive} to achieve real-time performance
requirements.  
%, due to the sharing of a computational resource (e.g.
%processor). And often, in particular for safety-critical applications, the execution order is
%completely determined at compile-time.

Previous work has not incorporated component execution times or ordering imposed by 
a component execution schedule. As a result, an analysis performed at the model level 
may produce results that deviate from the actual behavior of the system implemented 
from the model.  Our objective is to refine our compositional verification approach to capture 
this aspect of the design and ensure that analysis results faithfully represent the system 
implementation.  

% Brief overview of AADL
The Architecture Analysis and Design Language (AADL) was developed to capture the important 
design concepts in distributed real-time embedded systems~\cite{FeilerModelBasedEngineering2012}. 
%AADL is therefore well-suited for modeling avionics system architectures, and provides an excellent mechanism for capturing the important details of the system design. 
AADL captures both the hardware and software architecture in a hierarchical format,  
%It provides hardware component models including processors, buses, memories, and I/O devices, and software component models including threads, processes, and subprograms. 
%Interfaces for these components and data flows between components can also be defined. 
%The language offers a high degree of flexibility in terms of architecture and component detail. 
offering a high degree of flexibility and supporting incremental development 
in which an architecture is refined to add increasing levels of detail.
%This supports incremental development, where the architecture is refined to increasing levels of detail and where components can be refined with additional details over time. 
%AADL models can be built and managed using the Eclipse-based Open Source AADL Development Environment (OSATE) \cite{osate}. OSATE includes a number of tools for checking model characteristics, such as schedulability and data flows.  
%
% Need for compositional analysis - scalability, consistent with and supports development process, proof follows architecture
In AADL, an architecture model includes component interfaces, connections, and execution characteristics, but not component implementations. It describes the interactions between components and their arrangement in the system, but the lowest level 
components themselves are ``black boxes.'' Their implementations must be described separately using model-based behavioral specification languages or traditional programming languages, which may be included by reference in the architecture model.  
%This separation of implementation and architecture is an important factor in achieving scalability for the analysis tools that we have developed.

In previous work, we developed the Assume Guarantee Reasoning Environment (AGREE)~\cite{8625938}, a language and tool for compositional verification of AADL models.  The behavior of a model is described by {\em contracts} specified for each component.  A contract contains a set of {\em assumptions} about the component's inputs and a set of {\em guarantees} about the outputs.  The guarantees of a component must be true provided the component's assumptions are true.  The goal of an AGREE analysis is to prove that each component's contract is entailed by the contracts of its subcomponents.  Guarantees on a leaf-level component must be verified to hold by its implementation.  

AGREE was originally developed to reason about systems that execute synchronously. These systems have straightforward translations to \emph{Lustre}, a synchronous dataflow language interpreted by the model checkers used by AGREE. However, many systems that are modeled in AADL do not behave synchronously. Ideally one can implement a communication protocol between components, such as Physically Asynchronous Logically Synchronous (PALS)~\cite{pals}, that allows the abstraction of synchronous communication to be sound. However, for many systems this is not the case.

In this paper, we extend the AGREE framework to enable verification of \textit{scheduled} AADL models. We introduce virtual scheduling events, which tie AADL timing and scheduling semantics to AGREE contracts. This enhancement enables AGREE to take the software execution schedule into account in the analysis. Furthermore, it enables formal verification of a new class of embedded system architectures. 

This paper is organized as follows. First we illustrate the motivation of our work using simple examples in Section~\ref{example}. We then provide an informal description of our interpretation of the scheduling semantics in Section~\ref{overview}, followed by formal definitions of the model in Section~\ref{async}. We present the modeling of the semantics in the AGREE AADL annex and Lustre backend in Section~\ref{agree} and Section~\ref{lustre}, respectively. We demonstrate usage of the proposed model in a case study in Section~\ref{case-study}. Related work is presented in Section~\ref{rw}.  We discuss our conclusion and future work in Section~\ref{conclusion}.  